Time series clusters

### 2020-07-15 src/descriptive_Clusters.Rmd
descriptive_Clusters.Rmd now runs

LAD.cluster <- paste(path, "./data/temp/clusters.csv", sep = "")

@@

#summarise by LADs per cluster and Total tests / Mean speed per cluster
LAD.cluster.tests <- clusters %>%
  group_by(cluster.tests) %>%
  summarise(n.LADs = n())
LAD.cluster.testsTotal <- TS2020 %>%
  group_by(cluster.tests) %>%
  summarise(n.cluster = n())
LAD.cluster.tests <- left_join(LAD.cluster.tests, LAD.cluster.testsTotal)
LAD.cluster.up <- clusters %>%
  group_by(cluster.up) %>%
  summarise(up.LADs = n())
LAD.cluster.upMean <- summarise(group_by(TS2020, cluster.up),
  mean(speedup))
LAD.cluster.upSD <- summarise(group_by(TS2020, cluster.up),
  sd(speedup))
LAD.cluster.up <- cbind(LAD.cluster.up, LAD.cluster.upMean[,2], LAD.cluster.upSD[,2])
LAD.cluster.down <- clusters %>%
  group_by(cluster.down) %>%
  summarise(down.LADs = n())
LAD.cluster.downMean <- summarise(group_by(TS2020, cluster.down),
  mean(speeddown))
LAD.cluster.downSD <- summarise(group_by(TS2020, cluster.down),
  sd(speeddown))
LAD.cluster.down <- cbind(LAD.cluster.down, LAD.cluster.downMean[,2], LAD.cluster.downSD[,2])
LAD.cluster.diffUp <- clusters %>%
  group_by(cluster.up.diff) %>%
  summarise(diffUp.LADs = n())
LAD.cluster.diffDown <- clusters %>%
  group_by(cluster.down.diff) %>%
  summarise(diffDown.LADs = n())

@@

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

@@

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

LAD.cluster <- paste(path, "/data/temp/clusters_nodiff.csv", sep = "")

@@

#summarise by LADs per cluster and Total tests / Mean speed per cluster
LAD.cluster.tests <- clusters %>%
  group_by(cluster.tests) %>%
  summarise(n.LADs = n())
LAD.cluster.testsTotal <- TS2020 %>%
  group_by(cluster.tests) %>%
  summarise(n.cluster = n())
LAD.cluster.tests <- left_join(LAD.cluster.tests, LAD.cluster.testsTotal)
LAD.cluster.up <- clusters %>%
  group_by(cluster.up) %>%
  summarise(up.LADs = n())
LAD.cluster.upMean <- summarise(group_by(TS2020, cluster.up),
  mean(speedup))
LAD.cluster.upSD <- summarise(group_by(TS2020, cluster.up),
  sd(speedup))
LAD.cluster.up <- cbind(LAD.cluster.up, LAD.cluster.upMean[,2], LAD.cluster.upSD[,2])
LAD.cluster.down <- clusters %>%
  group_by(cluster.down) %>%
  summarise(down.LADs = n())
LAD.cluster.downMean <- summarise(group_by(TS2020, cluster.down),
  mean(speeddown))
LAD.cluster.downSD <- summarise(group_by(TS2020, cluster.down),
  sd(speeddown))
LAD.cluster.down <- cbind(LAD.cluster.down, LAD.cluster.downMean[,2], LAD.cluster.downSD[,2])

# commented to run the script
# LAD.cluster.diffUp <- clusters %>%
#   group_by(cluster.up.diff) %>%
#   summarise(diffUp.LADs = n())
# LAD.cluster.diffDown <- clusters %>%
#   group_by(cluster.down.diff) %>%
#   summarise(diffDown.LADs = n())

@@

@@

### 2020-07-15 src/ts_clusters.Rmd
descriptive_Clusters.Rmd now runs

# clusters data frame
clusters <- merge(cluster_up, cluster_down, by = "LAD")
names(clusters)[2] <- "cluster.up"
names(clusters)[3] <- "cluster.down"

@@

# save clusters file
out.clusters <- paste(path, "./data/temp/clusters.csv", sep = "")
write_csv(clusters, out.clusters)

>>>>

# all clusters data frame
clusters <- merge(cluster_up, cluster_down, by = "LAD")
names(clusters)[2] <- "cluster.up"
names(clusters)[3] <- "cluster.down"

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_all.csv", sep = "")
write_csv(clusters, out.clusters)

# clusters data frame WITHOUT the diff clusters
clusters.nodiff <- merge(cluster_up, cluster_down, by = "LAD")
names(clusters.nodiff)[2] <- "cluster.up"
names(clusters.nodiff)[3] <- "cluster.down"

clusters.nodiff <- merge(clusters.nodiff, cluster_tests, by = "LAD")
names(clusters.nodiff)[4] <- "cluster.tests"
#sapply(clusters, function(x) sum(is.na(x)))

clusters.nodiff  %>% arrange(cluster.up) %>% kable()

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_nodiff.csv", sep = "")
write_csv(clusters.nodiff, out.clusters)
